### 2020-06-19 magic_paper.tex
Comment on maximal subset of operations, replying to Nick.

\end{proof}
\nick{The above proposition is not relevant to $\sigma$-fragments where ``for any $\E_1 \not \in \O_\sigma$ and any $\E_2 \in \O_\sigma$'' we sometimes have $\E_1 \circ \E_2 \in \O_\sigma$ as well as $\E_2 \circ \E_1 \in \O_\sigma$ and sometimes $\E_1 \circ \E_2 \notin \O_\sigma$ as well as $\E_2 \circ \E_1 \notin \O_\sigma$}
As an immediate corollary of~\cref{thm:subproj}, a $\sigma$--fragment of any magic theory $\R$ is a contravariant fragment of $\R$.

>>>>

\end{proof}
\nick{The above proposition is not relevant to $\sigma$-fragments where ``for any $\E_1 \not \in \O_\sigma$ and any $\E_2 \in \O_\sigma$'' we sometimes have $\E_1 \circ \E_2 \in \O_\sigma$ as well as $\E_2 \circ \E_1 \in \O_\sigma$ and sometimes $\E_1 \circ \E_2 \notin \O_\sigma$ as well as $\E_2 \circ \E_1 \notin \O_\sigma$} \ddd{[Is this true? Act the combination of channels on $\sigma$. If it is a fixed point of only one of the channels then the composition cannot have it as a fixed point...thus the combination is in $\O_\sigma$ if and only if each of the channels is in $\O_\sigma$...right?]}
As an immediate corollary of~\cref{thm:subproj}, a $\sigma$--fragment of any magic theory $\R$ is a contravariant fragment of $\R$.
